### 2018-10-03 paper/paper.tex
update paper

Consider a single product one-stage flow-shop manufacturing system that releases orders from the
order pool into the production system by an external mechanism.
%
Usually the orders are released based on the observed (average) flow time of the last finished
orders. However, our method does not presuppose such an interdependence for detecting the lead time
syndrome as it works directly on (parts of) the \WIP{}-level of the system. Thus our approach is
also able to observe systematic releasing misbehavior, referred to as \LTS{}, which do not consider
the lead time as depended variable for the release decisions.
%
% Intuitively the method works as
% follows. By measuring the change of the average \WIP{}-level over time and comparing this to the
% average releases into the system it can infer the desired property.
%
We denote the demand rate at time $t \geqslant 0$ as $\dr{t}$, and the demand for the item during
the period defined by timestamps $t_{2} \geqslant t_{1} \geqslant 0$ as $\di{t_{1}}{t_{2}}$.
Similarly we denote the order release rate as $\rr{t}$ and the releases within a period as
$\ri{t_{1}}{t_{2}}$. Each work-station $i$ is equipped with a queue $\q_{i}$ on which released
orders are appended according to a given routing and from there handed over to the work-station if
only if the work-station is empty and the order is at the head of the queue. Thus we allow parallel
processing of unique orders with non-shared queues in the setup. In case of shared queues in this
single item setup the work-station shall be considered as a single work-station. The size of a queue
$\size{\q_{i}} \geqslant 0$ is given by the number of orders within the queue.

@@

  The queue size $\size{\Q_{i}}$ of stage $i$ is defined as
  $\size{\Q_{i}} = \sum_{i=1}^{n} \size{\q_{i}}$, where $n$ is the number of work-stations of stage
  $i$. Note that in this subsection we set $i=1$.

@@

As the demand may vary over time, e.g.~in a seasonal pattern or simply by some variance, it must be
considered as time factor in formulation of the lead time syndrome. To clarify, consider a seasonal
demand. It can clearly not be considered a lead time syndrome if the releases just depict the
demand. However

and therefore
specifies the

>>>>

Consider a single product one-stage flow-shop manufacturing system that releases orders from the
order pool into the production system by an external mechanism.
%
Usually the orders are released based on the observed (average) flow time of the last finished
orders. However, our method does not presuppose such an interdependence for detecting the lead time
syndrome as it works directly on (parts of) the \WIP{}-level of the system. Thus our approach is
also able to observe systematic releasing misbehavior, referred to as \LTS{}, which do not consider
the lead time as depended variable for the release decisions.
%
% Intuitively the method works as
% follows. By measuring the change of the average \WIP{}-level over time and comparing this to the
% average releases into the system it can infer the desired property.
%
We denote the demand rate at time $t \geqslant 0$ as $\dr{t}$ \MS[t]{rates needed?}, and the demand
for the item during the period defined by timestamps $t_{2} \geqslant t_{1} \geqslant 0$ as
$\di{t_{1}}{t_{2}}$. Similarly we denote the order release rate as $\rr{t}$ and the releases within
a period as $\ri{t_{1}}{t_{2}}$. Each work-station $i$ is equipped with a queue $\q_{i}$ on which
released orders are appended according to a given routing and from there handed over to the
work-station if only if the work-station is empty and the order is at the head of the queue. Thus we
allow parallel processing of unique orders with non-shared queues in the setup. In case of shared
queues in this single item setup the work-station shall be considered as a single work-station. The
size of a queue $\size{\q_{i}} \geqslant 0$ is given by the number of orders within the queue.

@@

  The \emph{queue size} $\size{\Q_{i}}$ of stage $i$ is defined as
  $\size{\Q_{i}} \defsym \sum_{i=1}^{n} \size{\q_{i}}$, where $n$ is the number of work-stations of stage
  $i$. Note that in this subsection we set $i=1$.

@@

As the demand may vary over time, e.g.~in a seasonal pattern or simply by some variance, it must be
considered as time factor in the formulation of the lead time syndrome. To clarify, consider a
seasonal demand. It can clearly not be considered a lead time syndrome if the releases just depict
the demand.

\MS{maybe use continuous representation below?}

Let the periodic demand be given by $\di{t}{t+1} = \max(0,\dmean(\frac{t+t+1}{2}) + \epsilon)$,
where $\dmean$ is a function which maps any given time $t \geqslant 0$ to the expected mean demand
at time $t$ and $\epsilon$ is drawn from a random variable $\X$ with mean $0$ and standard deviation
$\sigma$.

\begin{example}
  In case of a constant demand, $\dmean$ maps to a constant value, whereas for a seasonal demand $f$
  could be the sine-function.
  % In most cases we expect the random variable to be drawn from the
  % standard distribution $\X \sim \N{0}{\sigma^{2}}$ and in case of a discrete demand space applying
  % the nearest integer function.
\end{example}

% \MS{needed at all? we got the variance. But the max operator is used?}
% \begin{definition}
%   We define the \emph{standardised demand} $\dl{t}$ with time $t \geqslant 0$ as $\dl{t} \defsym
%   \di{t}{t+1} - \dmean(\frac{2t+1}{2})$. That is we subtract the mean from the demand to
%   be able to investigate the deviations solely.
%   % \begin{align*}
%   %   \dl{t} \defsym
%   %   \begin{cases}
%   %     1 + \epsilon & \text{iff }\dmean(\frac{2t+1}{2}) = 0\\
%   %     \dmean^{-1}(\frac{2t+1}{2}) \cdot \dmean(\frac{2t+1}{2}) + \epsilon & \text{otherwise}
%   %   \end{cases}
%   %   \tpkt
%   % \end{align*}
%   % Note that $\dmean(\cdot)$ is a scalar value and thus the inverse $\dmean^{-1}(\cdot)$ exists
%   % unless the mean demand is $0$.
% \end{definition}
% The standardised demand allows us to extract useful information from the deviations of the

We use the standard deviation $\sigma$ of the random variable $\X$ as measure for estimating the
time span being considered in our model. Recall that the standard deviation measures the expected
deviation of the mean in orders for one period.
%
Futhermore,... \MS[t]{seasonal stuff}
%

\begin{definition}
  We define the time span $\ts$ of the manufacturing system under investigation as
  \begin{align*}
    \ts \defsym \MS[t]{\text{seasonal stuff todo}} + \z \cdot 2 \sigma \tcom
  \end{align*}
  where $\z$ is a parameter.
\end{definition}

- je mehr variation im demand desto länger die zeit
